Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-04 paper/main.tex
add cf figs

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/ATT/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/ATT/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:att_prod_Russia}
\end{figure}

@@

@@

\begin{figure}[H] 
    \centering
    \caption{Impacts of Myanmar's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/ATT/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/ATT/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Myanmar's export restriction policy in 2014 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2014. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:att_prod_Myanmar}
\end{figure}

@@

>>>>

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/ATT/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/ATT/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:att_prod_Russia}
\end{figure}

@@

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/CF/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/CF/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:cf_prod_Russia}
\end{figure}

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/CF/imp_quant_Coniferous.png"}}
    \subfigure[][Non-conif Non-tropical]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/CF/imp_quant_Non-coniferous_non-tropical.png"}}
    \subfigure[][Non-conif Tropical]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Russia/CF/imp_quant_Non-coniferous_tropical.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:cf_imp_Russia}
\end{figure}

@@

\begin{figure}[H] 
    \centering
    \caption{Impacts of Myanmar's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/ATT/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/ATT/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Myanmar's export restriction policy in 2014 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2014. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:att_prod_Myanmar}
\end{figure}

@@

\begin{figure}[H] 
    \centering
    \caption{Impacts of Myanmar's Export Restriction on Its Trade Partners' Roundwood Production}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/CF/Production_Industrial_roundwood__coniferous.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 700, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/CF/Production_Industrial_roundwood__non-coniferous.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' production volumne of coniferous roundwood (a) and non-coniferous roundwood. X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:cf_prod_Myanmar}
\end{figure}

\begin{figure}[H] 
    \centering
    \caption{Impacts of Myanmar's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/CF/imp_quant_Coniferous.png"}}
    \subfigure[][Non-conif Non-tropical]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/CF/imp_quant_Non-coniferous_non-tropical.png"}}
    \subfigure[][Non-conif Tropical]{\includegraphics*[bb=0 0 650 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/syntheticDID/Myanmar/CF/imp_quant_Non-coniferous_tropical.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidential interval.}}
    \label{fig:cf_imp_Myanmar}
\end{figure}
